\label{1.1.7}

\begin{enumerate}[label = (\alph*)]
    \item Show that the following conditions are equivalent for a topological space X:
    \begin{enumerate}[label = (\roman*)]
        \item X is noetherian;
        
        \item every nonempty family of closed subsets has a minimal element;
        
        \item X satisfies the ascending chain condition for open subsets;
        
        \item every nonempty family of open subsets has a maximal element.
    \end{enumerate}
    
    \item A noetherian topological space is \textit{quasi-compact}, i.e., every open cover has a finite subcover.
    
    \item Any subset of a noetherian topological space is noetherian in its induced topology.
    
    \item A noetherian space which is also Hausdorff must be a finite set with the discrete topology.
\end{enumerate}

\begin{proof}
    \begin{enumerate}[label = (\alph*)]
        \item The equivalence of (i) and (ii) is the same argument from algebra. (i) is equivalent to (iii) and (ii) is equivalent to (iv) via taking complements, which reverses order.
        
        \item Let $X = \bigcup \mathcal U$ and let $S = \curly{\bigcup \mathcal V \mid \mathcal V \subseteq \mathcal U \text{ finite}}$. Then by (a), $S$ has a maximal element $U_1 \cup \dots \cup U_n$. If there is an $x \in X - (U_1 \cup \dots \cup U_n)$ then let $x \in U_{n + 1}$ open. Then $U_1 \cup \dots \cup U_n \subsetneq U_1 \cup \dots \cup U_{n + 1}$ a contradiction. Then $X = U_1 \cup \dots \cup U_n$ and $X$ is compact.
        
        \item Let $A \subseteq X$. Let $A_1 \supseteq A_2 \supseteq \dots$ be a decreasing chain of closed sets in $A$. Then $A_i = \overline{A_i} \cap A$ and $\overline{A_1} \supseteq \overline{A_2} \supseteq \dots$ is a decreasing chain in $X$, which is noetherian. The chain upstairs terminates so the chain downstairs does as well.
        
        \item Let $X$ be noetherian and Hausdorff. Let $A$ be an irreducible closed subset of $X$. Let $x, y \in A$ and $x \in U, y \in V$ open neighborhoods in $A$. $U \cap V \neq \emptyset$ by irreducibility, so $x = y$ by Hausdorffness. Thus, the irreducible components of $X$ are singletons and $X$ is finite. Finite Hausdorff spaces are discrete.
    \end{enumerate}
\end{proof}