\label{1.3.18}

\emph{Projectively Normal Varieties}

A projective variety $Y \subseteq \P^n$ is \emph{projectively normal} (with respect to the given embedding) if its homogeneous coordinate ring $S(Y)$ is integrally closed.

\begin{enumerate}[label = (\alph*)]
    \item If $Y$ is projectively normal then $Y$ is normal.

    \item There are normal varieties in projective space which are not projectively normal. For example, let $Y$ be the twisted quartic curve in $\P^3$ given parametrically by $(x, y, z, w) = (t^4, t^3 u, t^2 u^2, t u^3, u^4)$. Then $Y$ is normal by not projectively normal. See \ref{3.5.6} for more examples.

    \item Show that the twisted quartic curve $Y$ above is isomorphic to $\P^1$, which is projectively normal. Thus projective normality depends on the embedding.
\end{enumerate}

\begin{proof}
    \begin{enumerate}[label = (\alph*)]
        \item $\mathcal O_P \cong S(Y)_{(\m_P)}$ which should be normal. I cheated out of proving this in \ref{1.3.17}.a but maybe that same cheat works? Localization preserves integral closure but I'm not entirely sure what to do about the degree $0$ part. Somehow I expect this to work.

        \item This seems to satisfy the equation $xw = yz$, so hopefully when I finish \ref{1.3.17}.b that'll give me a proof. Also, I could just appeal to (c) to show that $Y$ is normal but this is not really wholly satisfying.

        \item Can we find an inverse ala the approach we took for the $d$-uple embedding? This is very close to that.
    \end{enumerate}
\end{proof}
